---
title: "Simple Linear Regression - activity02"
author: "Paul Warutumo"
date: "2024-01-25"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installing the libraries

```{r library-example, eval = FALSE}
  library(tidyverse)
  library(tidymodels)
  library(readr)
  library(dplyr)
  library(skimr)


```

## Loading the data

```{r}
hfi <- read_csv("hfi.csv")
```

#1. The dataset has 1458 rows and 123 columns
# Each row represent year iso-code and country

## Filtering the Year 2016 dataset 
```{r hfi-2016}

hfi_2016 <- hfi %>% filter(year == 2016)

hfi_2016
```

### Research Question
Predicting a country's personal freedom score in 2016

We shall get this by exploring the relationship between the personal freedom score, 'pf_score', and the political pressure and controls on media content index,'pf_expression_control'


```{r}
# Use ggplot2 for creating histograms

# Distribution of personal freedom scores (pf_score)
ggplot(hfi_2016, aes(x = pf_score)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Distribution of Personal Freedom Scores",
       x = "Personal Freedom Scores",
       y = "Frequency")

# Distribution of political pressures and controls on media content (pf_expression_control)
ggplot(hfi_2016, aes(x = pf_expression_control)) +
  geom_histogram(binwidth = 1, fill = "green", color = "black", alpha = 0.7) +
  labs(title = "Distribution of Political Pressures on Media Content",
       x = "Political Pressures and Controls",
       y = "Frequency")

```

### Summarry Statistics

```{r}
# Load necessary libraries
library(dplyr)
library(skimr)

# Summary statistics for personal freedom scores (pf_score)
summary_pf_score <- hfi_2016 %>%
  summarize(
    mean = mean(pf_score),
    median = median(pf_score),
    sd = sd(pf_score),
    min = min(pf_score),
    max = max(pf_score)
  )

# Detailed summary statistics for personal freedom scores
detailed_summary_pf_score <- skim(hfi_2016$pf_score)

# Summary statistics for political pressures and controls on media content (pf_expression_control)
summary_pf_expression_control <- hfi_2016 %>%
  summarize(
    mean = mean(pf_expression_control),
    median = median(pf_expression_control),
    sd = sd(pf_expression_control),
    min = min(pf_expression_control),
    max = max(pf_expression_control)
  )

# Detailed summary statistics for political pressures and controls on media content
detailed_summary_pf_expression_control <- skim(hfi_2016$pf_expression_control)

# Correlation between pf_score and pf_expression_control
correlation <- cor(hfi_2016$pf_score, hfi_2016$pf_expression_control)

# Print the results
print("Summary Statistics for Personal Freedom Scores:")
print(summary_pf_score)
cat("\nDetailed Summary Statistics for Personal Freedom Scores:\n")
print(detailed_summary_pf_score)

cat("\nSummary Statistics for Political Pressures on Media Content:")
print(summary_pf_expression_control)
cat("\nDetailed Summary Statistics for Political Pressures on Media Content:\n")
print(detailed_summary_pf_expression_control)

cat("\nCorrelation between pf_score and pf_expression_control:")
print(correlation)

```

